%-------------------------
% Resume in LaTeX - Sarvesh Style (1-Page Condensed)
% Author: Jay Hemnani
%-------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

% Page style
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Tighter margins for 1-page fit
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting - tighter spacing
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-3pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeExpHeading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1}, \textit{#3} & #2 \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.12in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}

%-------------------------------------------
% DOCUMENT START
%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Jay Hemnani} \\ \vspace{2pt}
    \small jayhemnani992000@gmail.com $|$ GitHub: \href{https://github.com/jayhemnani9910}{github.com/jayhemnani9910} \\
    San Jose, CA
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {San Jos\'{e} State University}{Jan 2025 -- Present $|$ San Jose, CA}
      {M.S. in Applied Data Intelligence}{}
      \resumeItemListStart
        \resumeItem{\textbf{Coursework:} Data Warehousing, Big Data Analytics, Distributed Systems, Data Visualization, Machine Learning.}
      \resumeItemListEnd
    \resumeSubheading
      {Pandit Deendayal Energy University (PDEU)}{2018 -- 2022 $|$ Gandhinagar, India}
      {B.Tech in Computer Engineering $|$ GPA: 8.7/10}{}
      \resumeItemListStart
        \resumeItem{\textbf{Coursework:} Software Development, Computer Vision, NLP, Big Data Analytics, Operating Systems.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeExpHeading
      {Data Analyst}{Summer 2025 $|$ San Jose, CA}
      {Elite Hotel Group}{}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{automated reporting pipelines} using SQL/Python, reducing manual effort by \textbf{40\%} and improving data consistency across multi-property analytics.}
        \resumeItem{Built \textbf{interactive dashboards} in Tableau/Power BI for occupancy, revenue, and KPI tracking; developed \textbf{demand forecasting models} using time-series analysis.}
      \resumeItemListEnd

    \resumeExpHeading
      {AI/ML Intern}{Jan -- May 2022 $|$ Gujarat, India}
      {Amnex}{}
      \resumeItemListStart
        \resumeItem{Built \textbf{credit fraud detection system} using ensemble ML (Random Forest, XGBoost) with SMOTE, achieving \textbf{94\% precision} on imbalanced transaction data.}
        \resumeItem{Developed \textbf{analytics dashboards} with statistical models for operational reporting, automating KPI calculations and anomaly detection.}
      \resumeItemListEnd

    \resumeExpHeading
      {iOS Development Intern}{Jun -- Aug 2021 $|$ Gujarat, India}
      {Cygnus SoftTech}{}
      \resumeItemListStart
        \resumeItem{Developed \textbf{CodeLock}, an iOS security app with AES encryption and secure local storage (Core Data), implementing \textbf{zero-knowledge architecture}.}
      \resumeItemListEnd

    \resumeExpHeading
      {Software Engineering Intern}{May -- Nov 2019 $|$ Gujarat, India}
      {Cactus Creatives}{}
      \resumeItemListStart
        \resumeItem{Built \textbf{cloud-native communication platform} for first responders on Azure; configured \textbf{CI/CD pipelines} reducing deployment time by \textbf{60\%}.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.12in, label={}]
    \small{\item{
     \textbf{Programming:} Python, SQL, Java, C++, Swift, Go, JavaScript \\
     \textbf{Data Engineering:} Pandas, PySpark, Airflow, Kafka, ETL/ELT Pipelines, Data Modeling \\
     \textbf{AI/ML \& Analytics:} Scikit-learn, TensorFlow, FAISS, LangChain, Feature Engineering, Statistical Analysis \\
     \textbf{Cloud \& DevOps:} AWS (S3, EC2, Lambda), GCP, Azure, Docker, Kubernetes, GitHub Actions (CI/CD) \\
     \textbf{Databases:} MySQL, PostgreSQL, MongoDB, TimescaleDB, Redis \\
     \textbf{Visualization:} Tableau, Power BI, Plotly, Streamlit, Dash
    }}
 \end{itemize}
 \vspace{-8pt}

%-----------PROJECTS-----------
\section{Academic Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Kayak --- Distributed Travel Metasearch} $|$ \emph{Node.js, MySQL, MongoDB, Redis, Kafka, Docker}}{}
          \resumeItemListStart
            \resumeItem{Engineered \textbf{3-tier distributed architecture} with API Gateway (JWT auth, rate limiting) routing to microservices for horizontal scaling.}
            \resumeItem{Achieved \textbf{sub-100ms search} via Redis caching; implemented Kafka event streaming for real-time inventory sync across services.}
            \resumeItem{Built \textbf{AI recommendation service} using LangChain agents for personalized travel deals based on user preferences.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{BarcaBrain --- Football Intelligence Platform} $|$ \emph{Python, Pandas, FAISS, Streamlit}}{}
          \resumeItemListStart
            \resumeItem{Designed \textbf{vector embedding pipeline} with feature engineering on match events, generating embeddings for 10,000+ players.}
            \resumeItem{Implemented \textbf{FAISS k-NN index} achieving \textbf{$<$100ms similarity search} with role/league filters for real-time scouting.}
            \resumeItem{Built \textbf{interactive scouting UI} displaying player clusters, comparisons, and attribute deltas for recruitment analysis.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Stock Data Platform --- Batch + Streaming Analytics} $|$ \emph{Python, Kafka, Airflow, TimescaleDB, Dash}}{}
          \resumeItemListStart
            \resumeItem{Built \textbf{distributed streaming architecture} using Kafka for real-time tick ingestion with idempotent writes.}
            \resumeItem{Orchestrated \textbf{Airflow ETL pipelines} for batch ingests, backfills, and validation with reproducible data lineage.}
            \resumeItem{Designed \textbf{TimescaleDB hypertables} with star schema powering Dash dashboards (SMA/EMA, intraday heatmaps).}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
