%-------------------------
% Data Analyst Resume - Jay Hemnani
%-------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

% Page style
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Tighter margins for 1-page fit
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-3pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeExpHeading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1}, \textit{#3} & #2 \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-8pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.12in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}

%-------------------------------------------
% DOCUMENT START
%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Jay Hemnani} \\ \vspace{2pt}
    \small jayhemnani992000@gmail.com $|$ GitHub: \href{https://github.com/jayhemnani9910}{github.com/jayhemnani9910} $|$ \href{https://jayhemnani.me}{jayhemnani.me} \\
    Gujarat, India (Open to Relocate)
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Pandit Deendayal Energy University (PDEU)}{2018 -- 2022 $|$ Gandhinagar, India}
      {B.Tech in Computer Engineering $|$ GPA: 8.7/10}{}
      \resumeItemListStart
        \resumeItem{\textbf{Coursework:} Statistics, Big Data Analytics, Database Systems, Business Intelligence.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.12in, label={}]
    \small{\item{
     \textbf{Programming:} Python, SQL (Advanced), R, JavaScript \\
     \textbf{Analytics \& Statistics:} Pandas, NumPy, Scikit-learn, Statistical Analysis, A/B Testing, Hypothesis Testing, Regression \\
     \textbf{Visualization \& BI:} Tableau, Power BI, Plotly, Streamlit, Dash, Excel (Advanced), Google Sheets \\
     \textbf{Databases:} PostgreSQL, MySQL, MongoDB, BigQuery, Data Warehousing, Data Modeling \\
     \textbf{Data Processing:} ETL/ELT Pipelines, Data Cleaning, Data Validation, Apache Airflow, dbt \\
     \textbf{Tools:} Git, Jupyter Notebooks, Google Analytics, Mixpanel, Looker
    }}
 \end{itemize}
 \vspace{-8pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeExpHeading
      {Data Analyst}{Summer 2025 $|$ San Jose, CA}
      {Elite Hotel Group}{}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{automated reporting pipelines} using SQL and Python, reducing manual reporting effort by \textbf{40\%} and improving data consistency across multi-property analytics.}
        \resumeItem{Designed and deployed \textbf{interactive dashboards} in Tableau and Power BI for occupancy, revenue, and KPI tracking, enabling data-driven decision-making for revenue management.}
        \resumeItem{Developed \textbf{demand forecasting models} using time-series analysis and regression techniques, improving booking prediction accuracy to support dynamic pricing strategies.}
      \resumeItemListEnd

    \resumeExpHeading
      {Technical Consultant}{2022 -- 2024 $|$ Remote}
      {}{}
      \resumeItemListStart
        \resumeItem{Provided \textbf{data analytics consulting} for small businesses, building dashboards, A/B testing frameworks, and reporting automation for business intelligence.}
      \resumeItemListEnd

    \resumeExpHeading
      {AI/ML Intern}{Jan -- May 2022 $|$ Gujarat, India}
      {Amnex}{}
      \resumeItemListStart
        \resumeItem{Built \textbf{fraud detection analytics} using ensemble ML models achieving \textbf{94\% precision}, presenting findings to stakeholders with actionable recommendations.}
        \resumeItem{Developed \textbf{analytics dashboards} with statistical models for operational reporting, automating KPI calculations and anomaly detection across business metrics.}
      \resumeItemListEnd

    \resumeExpHeading
      {Software Engineering Intern}{May -- Nov 2019 $|$ Gujarat, India}
      {Cactus Creatives}{}
      \resumeItemListStart
        \resumeItem{Built \textbf{data pipelines and reporting tools} for internal analytics; configured automated workflows reducing manual effort by \textbf{60\%}.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Stock Data Platform --- Financial Analytics Dashboard} $|$ \emph{Python, SQL, Airflow, TimescaleDB, Dash}}{}
          \resumeItemListStart
            \resumeItem{Built \textbf{interactive financial dashboards} in Dash displaying rolling indicators (SMA, EMA), intraday heatmaps, and time-window filtering for market analysis.}
            \resumeItem{Designed \textbf{ETL pipelines} with Airflow for automated data ingestion, validation, and transformation with reproducible data lineage.}
            \resumeItem{Created \textbf{star schema data model} (FactPrices + dimensions) optimized for analytical queries and dashboard performance.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{BarcaBrain --- Sports Analytics Platform} $|$ \emph{Python, Pandas, Streamlit, Plotly}}{}
          \resumeItemListStart
            \resumeItem{Designed \textbf{analytics dashboard} for player comparison and scouting, displaying clusters, similarity scores, and attribute deltas for 10,000+ players.}
            \resumeItem{Built \textbf{feature engineering pipeline} transforming raw match events into actionable metrics for recruitment analysis.}
            \resumeItem{Created \textbf{interactive visualizations} enabling rapid like-for-like player discovery with filtering by role, league, and performance metrics.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Indian Crime Data Analytics} $|$ \emph{Python, SQL, Pandas, Visualization}}{}
          \resumeItemListStart
            \resumeItem{Built \textbf{analytical pipeline} for pattern mining across crime incident categories, identifying trends and correlations in multi-year datasets.}
            \resumeItem{Designed \textbf{interactive visualizations} and statistical summaries for incident forecasting and resource allocation recommendations.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
