%-------------------------
% ML Engineer Resume - Jay Hemnani
%-------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

% Page style
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Tighter margins for 1-page fit
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-3pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeExpHeading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1}, \textit{#3} & #2 \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-8pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.12in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}

%-------------------------------------------
% DOCUMENT START
%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Jay Hemnani} \\ \vspace{2pt}
    \small jayhemnani992000@gmail.com $|$ GitHub: \href{https://github.com/jayhemnani9910}{github.com/jayhemnani9910} $|$ \href{https://jayhemnani.me}{jayhemnani.me} \\
    Gujarat, India (Open to Relocate)
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Pandit Deendayal Energy University (PDEU)}{2018 -- 2022 $|$ Gandhinagar, India}
      {B.Tech in Computer Engineering $|$ GPA: 8.7/10}{}
      \resumeItemListStart
        \resumeItem{\textbf{Coursework:} Computer Vision, Natural Language Processing, Big Data Analytics, Neural Networks.}
        \resumeItem{\textbf{Publications:} 2 IEEE papers --- Diabetes Prediction (Stacking Classifier), CPU Scheduling Analysis.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.12in, label={}]
    \small{\item{
     \textbf{Programming:} Python, SQL, Java, C++, JavaScript/TypeScript \\
     \textbf{ML/AI Frameworks:} PyTorch, PyTorch Geometric, TensorFlow, Scikit-learn, Hugging Face Transformers, YOLOv8 \\
     \textbf{ML Engineering:} FAISS, LangChain, LangGraph, Vector Databases (Pinecone, ChromaDB), RAG Pipelines, Feature Engineering \\
     \textbf{Data Processing:} Pandas, NumPy, PySpark, Apache Kafka, Airflow \\
     \textbf{Cloud \& MLOps:} AWS (SageMaker, Lambda, S3), Docker, Kubernetes, MLflow, DVC, Weights \& Biases \\
     \textbf{Databases:} PostgreSQL, MongoDB, Redis, TimescaleDB, ChromaDB, Pinecone
    }}
 \end{itemize}
 \vspace{-8pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeExpHeading
      {Data Analyst}{Summer 2025 $|$ San Jose, CA}
      {Elite Hotel Group}{}
      \resumeItemListStart
        \resumeItem{Developed \textbf{demand forecasting models} using time-series analysis and regression techniques, improving booking prediction accuracy for dynamic pricing optimization.}
        \resumeItem{Built \textbf{automated ML pipelines} for KPI prediction and anomaly detection across multi-property analytics workflows.}
      \resumeItemListEnd

    \resumeExpHeading
      {Technical Consultant}{2022 -- 2024 $|$ Remote}
      {}{}
      \resumeItemListStart
        \resumeItem{Provided \textbf{ML and data analytics consulting} for small businesses, building predictive models, A/B testing frameworks, and automation solutions.}
      \resumeItemListEnd

    \resumeExpHeading
      {AI/ML Intern}{Jan -- May 2022 $|$ Gujarat, India}
      {Amnex}{}
      \resumeItemListStart
        \resumeItem{Built \textbf{credit fraud detection system} using ensemble ML (Random Forest, XGBoost) with SMOTE for class imbalance, achieving \textbf{94\% precision} on imbalanced transaction data.}
        \resumeItem{Developed \textbf{statistical models} for operational reporting, automating anomaly detection and KPI forecasting pipelines.}
      \resumeItemListEnd

    \resumeExpHeading
      {Software Engineering Intern}{May -- Nov 2019 $|$ Gujarat, India}
      {Cactus Creatives}{}
      \resumeItemListStart
        \resumeItem{Built \textbf{cloud-native backend services} on Azure; configured \textbf{CI/CD pipelines} reducing deployment time by \textbf{60\%}.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Soccer Vision Research --- Multi-Model Sports Analytics} $|$ \emph{Python, PyTorch, RF-DETR, SAM2, W\&B}}{}
          \resumeItemListStart
            \resumeItem{Built \textbf{modular CV pipeline} combining 4 SOTA models (RF-DETR for detection, SAM2 for segmentation, SigLIP for classification, ByteTrack for tracking) with configurable model swapping.}
            \resumeItem{Implemented \textbf{experiment tracking} with Weights \& Biases for systematic benchmarking across model configurations and hyperparameter sweeps.}
            \resumeItem{Designed \textbf{extensible architecture} enabling rapid experimentation --- new model variants integrate via standardized interface without pipeline changes.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Nobel Data Intelligence --- Graph Neural Networks} $|$ \emph{Python, PyTorch Geometric, BioPython, RDKit}}{}
          \resumeItemListStart
            \resumeItem{Built \textbf{GNN-based molecular property prediction} framework processing 10K+ compounds with PyTorch Geometric for graph-level regression tasks.}
            \resumeItem{Integrated \textbf{bioinformatics toolkits} (ProDy, BioPython, RDKit) for feature extraction from protein structures and molecular graphs.}
            \resumeItem{Designed \textbf{extensible data pipeline} converting molecular SMILES to graph representations with configurable node/edge feature engineering.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{BarcaBrain --- Vector Search Intelligence} $|$ \emph{Python, FAISS, LangChain, Streamlit}}{}
          \resumeItemListStart
            \resumeItem{Designed \textbf{vector embedding pipeline} with feature engineering on match events, generating dense embeddings for 10,000+ players.}
            \resumeItem{Implemented \textbf{FAISS k-NN index} for semantic similarity search achieving \textbf{$<$100ms latency} with hybrid filtering for role/league constraints.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
