%-------------------------
% Software Engineer Resume - Jay Hemnani
%-------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

% Page style
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Tighter margins for 1-page fit
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-3pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeExpHeading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1}, \textit{#3} & #2 \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-8pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.12in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}

%-------------------------------------------
% DOCUMENT START
%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Jay Hemnani} \\ \vspace{2pt}
    \small jayhemnani992000@gmail.com $|$ GitHub: \href{https://github.com/jayhemnani9910}{github.com/jayhemnani9910} $|$ \href{https://jayhemnani.me}{jayhemnani.me} \\
    Gujarat, India (Open to Relocate)
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Pandit Deendayal Energy University (PDEU)}{2018 -- 2022 $|$ Gandhinagar, India}
      {B.Tech in Computer Engineering $|$ GPA: 8.7/10}{}
      \resumeItemListStart
        \resumeItem{\textbf{Coursework:} Operating Systems, Computer Networks, Database Systems, Software Development.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.12in, label={}]
    \small{\item{
     \textbf{Languages:} Python, Java, Go, JavaScript/TypeScript, C++, SQL \\
     \textbf{Backend:} Node.js, Express, FastAPI, REST APIs, GraphQL, gRPC, Microservices Architecture \\
     \textbf{Distributed Systems:} Apache Kafka, Redis, Message Queues, Event-Driven Architecture, Load Balancing \\
     \textbf{Databases:} PostgreSQL, MySQL, MongoDB, Redis, TimescaleDB, Database Design \& Indexing \\
     \textbf{Cloud \& DevOps:} AWS (EC2, S3, Lambda, ECS), Azure, Docker, Kubernetes, GitHub Actions, CI/CD \\
     \textbf{Tools:} Git, Linux, Nginx, JWT/OAuth, API Gateway, Prometheus, Rate Limiting
    }}
 \end{itemize}
 \vspace{-8pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeExpHeading
      {Data Analyst}{Summer 2025 $|$ San Jose, CA}
      {Elite Hotel Group}{}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{automated data pipelines} using Python and SQL, reducing manual processing by \textbf{40\%} and improving system reliability across multi-property workflows.}
        \resumeItem{Built \textbf{REST APIs} for internal dashboards integrating with Tableau/Power BI for real-time KPI tracking.}
      \resumeItemListEnd

    \resumeExpHeading
      {Technical Consultant}{2022 -- 2024 $|$ Remote}
      {}{}
      \resumeItemListStart
        \resumeItem{Provided \textbf{backend development and infrastructure consulting} for small businesses, building APIs, deployment pipelines, and automation solutions.}
      \resumeItemListEnd

    \resumeExpHeading
      {AI/ML Intern}{Jan -- May 2022 $|$ Gujarat, India}
      {Amnex}{}
      \resumeItemListStart
        \resumeItem{Built \textbf{fraud detection backend} using Python with REST APIs for model serving, achieving \textbf{94\% precision} on transaction classification.}
        \resumeItem{Developed \textbf{automated reporting services} with scheduled jobs and database integrations for operational analytics.}
      \resumeItemListEnd

    \resumeExpHeading
      {Software Engineering Intern}{May -- Nov 2019 $|$ Gujarat, India}
      {Cactus Creatives}{}
      \resumeItemListStart
        \resumeItem{Built \textbf{cloud-native communication platform} for first responders using microservices architecture on Azure with REST APIs for real-time dispatch.}
        \resumeItem{Configured \textbf{CI/CD pipelines} with automated testing and deployment workflows, reducing deployment time by \textbf{60\%}.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Kayak --- Distributed Travel Platform} $|$ \emph{Node.js, MySQL, MongoDB, Redis, Kafka, Docker}}{}
          \resumeItemListStart
            \resumeItem{Engineered \textbf{3-tier distributed architecture} with API Gateway handling JWT authentication, rate limiting, and request routing to independent microservices.}
            \resumeItem{Designed \textbf{horizontal scaling strategy} with independent User, Search, and Booking services for fault isolation and independent deployment.}
            \resumeItem{Achieved \textbf{sub-100ms API latency} via Redis caching; implemented \textbf{Kafka event streaming} for real-time inventory sync across services.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Airbnb --- Cloud-Native Booking Platform} $|$ \emph{React, Node.js, MongoDB, Kafka, Docker, K8s}}{}
          \resumeItemListStart
            \resumeItem{Built \textbf{full-stack booking platform} with React frontend and Node.js microservices, deployed on Kubernetes with auto-scaling and health monitoring.}
            \resumeItem{Implemented \textbf{Kafka-based event bus} for asynchronous communication between booking, search, and notification services.}
            \resumeItem{Integrated \textbf{AI-powered travel planning} using LangChain agents for personalized recommendations within the booking workflow.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{CAG Deep Research --- Multi-Agent System} $|$ \emph{Python, LangGraph, FastAPI, PostgreSQL}}{}
          \resumeItemListStart
            \resumeItem{Architected \textbf{multi-agent orchestration system} with LangGraph, coordinating 5+ specialized AI agents to autonomously synthesize research reports.}
            \resumeItem{Built \textbf{FastAPI backend} with PostgreSQL persistence, handling concurrent agent workflows with state management and retry logic.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
